%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
   
    
%---------------------------------------------------------
  \cventry
    {Coalfire} % Organization
    {Penetration Tester - Intern} % Job title
    {Sterling, VA} % Location
    {Jun. 2018 - Aug 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Performed \keyword{PCI Testing} for government and private companies.}
	  \item {Detected and exploited \keyword{CVE's} on contracted networks containing sensitive health and financial data.}
      \item {Practiced physical entry vulnerabilities and developed \keyword{HID Attack} payloads as a research venture.}
      \end{cvitems}
    }
   
%-----------------------------------------------------------
  \cventry
    {Iglesias-Prieto Laboratories} % Organization
    {Automation Engineer and Technician} % Job title
    {State College, PA \& Mexico} % Location
    {Jan. 2016 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created an admistrative dashboard with a \keyword{mySQL} database for metrics analysis and \keyword{predictive trend spotting}}
	\item {Engineered and automated a >\$6,000 lab for coral bleaching research using \keyword{Arduino} for low-level electronics, \keyword{Raspberry Pi} for efficient networking, and \keyword{Django} for fast and secure websites. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Rain Reality}
    {Lead Web Developer} % Job title
    {Remote} % Location
    {Oct. 2016 - Jan. 2018 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item { Led a team of 3 remote developers in a high-paced startup environment} 
      \item {Engineered a 3d scene builder web app for augmented reality solutions in the classroom using \keyword{three.js} and \keyword{Unity}}
      \end{cvitems}
    }
\end{cventries}
